### 2016-05-30 intro.tex
syntax work
cheers

Continuing on this point, it seems that the coins of~$\mathbf{B}_1$ (whatever their use) are intended to be kept secret from the adversary.  Thus, to the extent that it addresses real Bloom filters at all, the NY security notion only addresses applications in which the representation is created using secret coins.  But many real-world applications of Bloom filters have no secrets.  NY point to web proxies, which use Bloom filters to compactly represent the objects they store locally, as motivation for their work.  But real web proxies like Squid~\cite{xxx} do \emph{not} use secrets in their Bloom filters.  They use the basic Bloom filter with four hash functions, defined as follows: $h_1(x) = \mathrm{MD5}(x)[0,\ldots,31]$, $h_2(x)=\mathrm{MD5}(x)[32,\ldots,63]$, $h_3(x)=\mathrm{MD5}(x)[64,\ldots,95]$, and $h_4(x)=\mathrm{MD5}(x)[96,\ldots,127]$.  Likewise, there are no secrets in the Bloom filters used by Google's BigTable~\cite{xxx}, HBase~\cite{xxx}, \tsnote{make an impressive list.}  There are applications in which the proposed Bloom filter instantiations do use secretly keyed hash functions, e.g. $h_j(x) = (f(K_0,x) + j\cdot g(K_1,x))\bmod m$, where $j\in[1,k]$, $m$ is the number of bits in the array, and where $f,g$ are PRFs keyed by secrets $K_0,K_1$.  This particular ``encrypted Bloom filter'' instantiation was suggested for use in efficient linking of records across separate medical record databases~\cite{xxx}.  (It was subsequently shown not to be secure by Niedermeier et al.~\cite{xxx}, where a clever use of frequency analysis recovered the last names of patients given access only to the Bloom filter array.)  In any case, it is clear that the NY definition does not capture the most widely used applications of Bloom filters, e.g. CDN summary caches, P2P network routing algorithms, etc.

@@

\tsnote{Stopped here.}

>>>>

Continuing on this point, it seems that the coins of~$\mathbf{B}_1$ (whatever their use) are intended to be kept secret from the adversary.  Thus, to the extent that it addresses real Bloom filters at all, the NY security notion only addresses applications in which the representation is created using secret coins.  But many real-world applications of Bloom filters have no secrets.  NY point to web proxies, which use Bloom filters to compactly represent the objects they store locally, as motivation for their work.  But real web proxies like Squid~\cite{xxx} do \emph{not} use secrets in their Bloom filters.  They use the basic Bloom filter with four hash functions, defined as follows: $h_1(x) = \mathrm{MD5}(x)[0,\ldots,31]$, $h_2(x)=\mathrm{MD5}(x)[32,\ldots,63]$, $h_3(x)=\mathrm{MD5}(x)[64,\ldots,95]$, and $h_4(x)=\mathrm{MD5}(x)[96,\ldots,127]$.  Likewise, there are no secrets in the Bloom filters used by Google's BigTable~\cite{xxx}, HBase~\cite{xxx}, \tsnote{make an impressive list.}  There are applications in which the proposed Bloom filter instantiations do use secretly keyed hash functions, e.g. $h_j(x) = (f(K_0,x) + j\cdot g(K_1,x))\bmod m$, where $j\in[1,k]$, $m$ is the number of bits in the array, and where $f,g$ are PRFs keyed by secrets $K_0,K_1$.  This particular ``encrypted Bloom filter'' instantiation was suggested for use in efficient linking of records across separate medical record databases~\cite{xxx}.  (It was subsequently shown not to be secure by Niedermeier et al.~\cite{xxx}, where a clever use of frequency analysis recovered the last names of patients given access only to the Bloom filter array.\tsnote{This shows that having secret hash functions does not automatically give privacy.})  In any case, it is clear that the NY definition does not capture the most widely used applications of Bloom filters, e.g. CDN summary caches, P2P network routing algorithms, etc.

@@
